### 2019-11-22 README.rmd
change 'diagram' to 'plot' + debug infer-label param

This is a [**ggplot2** extension](http://www.ggplot2-exts.org/) for alluvial diagrams.

@@

The alluvial plots implemented here can be used to visualize frequency distributions over time or frequency tables involving several categorical variables. The design is derived mostly from the [**alluvial**](https://github.com/mbojan/alluvial) package, but the **ggplot2** framework induced several conspicuous differences:

- **alluvial** understands a variety of inputs (vectors, lists, data frames), while **ggalluvial** requires a single data frame;
- **alluvial** uses each variable of these inputs as a dimension of the data, whereas **ggalluvial** requires the user to specify the dimensions, either as separate aesthetics or as [key-value pairs](http://tidyr.tidyverse.org/);
- **alluvial** produces both the *alluvia*, which link cohorts across multiple dimensions, and (what are here called) the *strata*, which partition the data along each dimension, in a single function; whereas **ggalluvial** relies on separate layers (stats and geoms) to produce strata, alluvia, and alluvial segments called *lodes* and *flows*.

@@

Development versions can be installed from GitHub:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", build_vignettes = TRUE)
```
The
[optimization branch](https://github.com/corybrunson/ggalluvial/tree/optimization) contains a development version with experimental functions to reduce the number or area of alluvial overlaps (see issue [#6](https://github.com/corybrunson/ggalluvial/issues/6)). Install it as follows:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", ref = "optimization")
```

@@

Here is how to generate an alluvial diagram representation of the multi-dimensional categorical dataset of passengers on the Titanic:

>>>>

This is a [**ggplot2** extension](http://www.ggplot2-exts.org/) for alluvial plots.

@@

The alluvial plots implemented here can be used to visualize frequency distributions over time or frequency tables involving several categorical variables. The design is inspired by the [**alluvial**](https://github.com/mbojan/alluvial) package, but the **ggplot2** framework induced several conspicuous differences:

- **alluvial** understands a variety of inputs (vectors, lists, data frames), whereas **ggalluvial** requires a single data frame;
- **alluvial** uses each variable of these inputs as a dimension of the data, whereas **ggalluvial** requires the user to specify the dimensions, either as separate aesthetics or as [key-value pairs](http://tidyr.tidyverse.org/);
- **alluvial** produces both the *alluvia*, which link cohorts across multiple dimensions, and (what are here called) the *strata*, which partition the data along each dimension, in a single function; whereas **ggalluvial** relies on separate layers (stats and geoms) to produce strata, alluvia, and alluvial segments called *lodes* and *flows*.

Additionally, **ggalluvial** arranges these layers vertically without gaps, so that the secondary plotting axis indicates the cumulative values of the strata at each dimension.

@@

Development versions can be installed from GitHub:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", build_vignettes = TRUE)
```
The
[optimization branch](https://github.com/corybrunson/ggalluvial/tree/optimization) contains a development version with experimental functions to reduce the number or area of alluvial overlaps (see issue [#6](https://github.com/corybrunson/ggalluvial/issues/6)). Install it as follows:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", ref = "optimization")
```
Note, however, that this branch has not kept pace with the `master` branch or with recent upgrades on CRAN.

@@

Here is how to generate an alluvial plot representation of the multi-dimensional categorical dataset of passengers on the Titanic:
